Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Correct typos where there were double "(" and ")"

Data were visualised using 'ggplot2' ((version `r packageVersion("ggplot2")`)) [@Wickham2016], 'ggpubr' ((version `r packageVersion("ggpubr")`)) [@Kassambara2020] and patchwork ((version `r packageVersion("patchwork")`)) [@Pedersen2020].

>>>>

Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].
